\plaintitle

### 2017-01-09 drafts/labor/introduction.tex
table v2

>>>>

\begin{table*}[t]
  \centering
  \begin{tabularx}{\textwidth}{l X X X}
    \toprule
    & \textit{Observations in piecework} & \textit{Mechanism} & \textit{Implications for On--demand Work} \\
    \midrule
    Complexity &
    \small{Growth from simple tasks such as sewing to more complex composite outcomes on the assembly line floor.} &
    \small{Complexity was limited by what could be easily measured and evaluated for payment by the piece.} &
    \small{Measurement and verification remain challenges and will limit complexity unless solved.} \\ \hline

    Decomposition &
    \small{Work began sliced such that non-experts could perfom each piece, but over time was sliced such that non-overlapping expertise was required for each step.} &
    \small{Scientific Management and Taylorism informed and drove decomposition by measuring and facilitating the optimization of smaller tasks.} &
    \small{After scientific management matured, piecework began  specialized training to create experts in narrow tasks. A similar shift seems feasible with on--demand work.} \\ \hline
    %The research has reached an ``atomic'' level of decomposition, exhausting the cognitive limits of the human brain, past which point task--switching becomes a substantial cost.} \\ \hline

    Workers &
    \small{Firms antagonized and exploited workers, leading workers to support one another independently, ultimately resulting in strong advocacy groups counterbalancing firms.} &
    \small{The features of piecework (independence and transience) were both the fulcrum managers used to exploit workers as well as the focal point around which workers bonded.} &
    \small{While worker frustrations are similar, the decentralized nature of on--demand work will limit collective action until there exist platforms to coordinate and exert pressure.} \\ 
    \bottomrule
  \end{tabularx}
  \caption{Piecework and on--demand work have both wrestled with questions of how complex work can get, how finely-sliced tasks can become, and what the workplace looks like for workers. We connect piecework's history (left) to the mechansims that impacted it (center) to derive predictions for modern on--demand work (right). }
\end{table*}
